\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Page Piccinini}{www.pagepiccinini.com}{page.piccinini@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Objective
%\header{Objective}

%\begin{body}
%	\vspace{14pt}
%	To get a job
%\end{body}

%\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
\header{Research Interests}

\begin{body}
	\vspace{14pt}
	Bilingualism, psycholinguistics, phonetics, speech perception, speech production, code-switching, accented speech
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{Ph.D. Linguistics} \hfill \emph{2016} \\
	\emph{University of California, San Diego}, La Jolla, CA \\
	\underline{Thesis:} Cross-language Activation and the Phonetics of Code-switching\\
  \medskip

	\textbf{M.A. Linguistics} \hfill \emph{2009} \\
	\emph{Northwestern University}, Evanston, IL\\
	\underline{Thesis:} Semantic Contextual Cues and Listener Adaptation to Foreign-Accented English\\
  \medskip

	\textbf{B.A. Linguistics} \hfill \emph{2009} \\
	\textbf{B.A. International Studies} \\
	\emph{Northwestern University}, Evanston, IL\\
	\underline{Academic Honors:} Cum laude, Dean's List Quarters Fall 2005 - Fall 2007\\

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Experience
\header{Research Experience}

\begin{body}
	\vspace{14pt}
	\textbf{Postdoctoral Researcher}, \emph{NeuroPsychologie Interventionnelle (NPI)} \hfill \emph{2016 - 2017}\\
	D\'epartement d'Etudes Cognitives (DEC), Ecole Normale Sup\'erieure, Paris, France
	\medskip
	
	\textbf{Graduate Student Lab Member}, \emph{Phonetics Lab} \hfill \emph{2010 - 2016}\\
	Department of Linguistics, University of California, San Diego, La Jolla, CA\\
 	\medskip
	
	\textbf{Engineer}, \emph{NeuroPsychologie Interventionnelle (NPI)} \hfill \emph{2015 - 2016}\\
	D\'epartement d'Etudes Cognitives (DEC), Ecole Normale Sup\'erieure, Paris, France
	\medskip
	
	\textbf{Visiting Researcher}, \emph{Laboratoire de Sciences Cognitives et Psycholinguistique (LSCP)} \hfill \emph{2014 - 2015}\\
	D\'epartement d'Etudes Cognitives (DEC), Ecole Normale Sup\'erieure, Paris, France
	\medskip
	
	\textbf{Visiting Researcher}, \emph{The GrEP Group} \hfill \emph{2011}\\
	Department of Translation and Language Sciences, Universitat Pompeu Fabra, Barcelona, Spain
	\medskip
	
	\textbf{Research Assistant}, \emph{Speech Communication Research Group} \hfill \emph{2006 - 2009}\\
	Department of Linguistics, Northwestern University, Evanston, IL
\end{body}

\smallskip

% \newpage{} % uncomment this line if you want to force a new page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Publications}

\begin{body}
	\vspace{14pt}
	
	\textbf{Piccinini, P.}, Arvaniti, A. (2019). ``Dominance, mode, and individual variation in bilingual speech production and perception." \emph{Linguistic Approaches to Bilingualism}, Online First Article.\\
	\medskip
	
	Politzer-Ahles, S., \textbf{Piccinini, P.} (2018). ``On visualizing phonetic data from repeated measures experiments with multiple random effects." \emph{Journal of Phonetics}, 70, 56-69.\\
	\medskip
	
	Bergmann, C., Tsuji, S., \textbf{Piccinini, P. E.},  Lewis, M. L.,  Braginsky, M., Frank, F. C., Cristia, A. (2018). ``Promoting replicability in developmental research through meta-analyses: Insights from language acquisition research." \emph{Child Development}, 89(6), 1996-2009.\\
	\medskip
	
	Tsuji, S., Bergmann, C., Lewis, M.,  Braginsky, M.,  \textbf{Piccinini, P.},  Frank, F. C., Cristia, A. (2017). ``MetaLab: A repository for meta-analyses on language development, and more." 	\emph{Proceedings of Interspeech 2017}, 2038-2039.\\
	\medskip
	
	Lewis, M., Braginsky, M., Tsuji, S., Bergmann, C., \textbf{Piccinini, P. E.}, Cristia, A., Frank, M. C. (2016). ``A quantitative synthesis of early language acquisition using meta-analysis." \emph{PsyArXiv}, 21, Web.\\
	\medskip
		
	Armstrong, M., \textbf{Piccinini, P.}, Ritchart, A. (2016). ``Non-question rises in narratives produced by mothers and daughters." \emph{Proceedings of the 8th Speech Prosody Conference}.\\
	\medskip
	
	Chung, Y., \textbf{Piccinini, P.}, Rose, S. (2016). ``The interaction of polar question and declarative intonation with lexical tone in Moro." \emph{Proceedings of the 8th Speech Prosody Conference}.\\
	\medskip

	\textbf{Piccinini, P.}, Arvaniti, A. (2015). ``Voice onset time in Spanish-English spontaneous code-switching." \emph{Journal of Phonetics}, 52, 121-137.\\
	\medskip

	\textbf{Piccinini, P.}, Arvaniti, A. (2015). ``Voice onset time in Spanish-English spontaneous code-switching." \emph{Proceedings of the 18th International Congress of Phonetic Sciences}.\\
	\medskip
	
	Armstrong, M., \textbf{Piccinini, P.}, Ritchart, A. (2015). ``The phonetics and distribution of non-question rises in two varieties of American English." \emph{Proceedings of the 18th International Congress of Phonetic Sciences}.\\
	\medskip
	
	\textbf{Piccinini, P.}, Garellek, M. (2014). ``Prosodic cues to monolingual versus code-switching sentences in English and Spanish." \emph{Proceedings of the 7th Speech Prosody Conference}.\\
	\medskip
	
	\textbf{Piccinini, P.}, Arvaniti, A. (2014). ``Accessing cross language categories in learning a third language.'' \emph{Proceedings of the 38th Boston University Conference on Language Development}.\\
	 \medskip

	\textbf{Piccinini, P.}, Kramer, E. (2013). ``Unsupervised machine learning for the accurate classification of the discourse marker \emph{like} in code-switching utterances.'' \emph{Proceedings of Meetings on Acoustics (POMA)}, 19(060007).\\
	 \medskip
	
	Grijalva, C., \textbf{Piccinini, P.}, Arvaniti, A. (2013). ``The vowel spaces of Southern Californian English and Mexican Spanish as produced by monolinguals and bilinguals.'' \emph{Proceedings of Meetings on Acoustics (POMA)}, 19(060088).\\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited Presentations
\header{Invited Presentations}

\begin{body}
	\vspace{14pt}

	\textbf{Piccinini, P.} (2013). ``Accessing cross language categories in learning a third language.''  Department of Languages, Literatures \& Cultures, Spanish \& Portuguese program, University of Massachusetts-Amherst. Amherst, MA. (October)\\
	\medskip
	
	\textbf{Piccinini, P.} (2013). ``Accessing cross language categories in learning a third language.''  Center for Research in Language, University of California, San Diego. La Jolla, CA. (May)\\
	\medskip
	
	\textbf{Piccinini, P.} (2011). ``The gradient  production of Spanish-English code-switching.''  Center for Research in Language, University of California, San Diego. La Jolla, CA. (October)\\
	\medskip
	
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conferences Presentations

\header{Conference Presentations}

\begin{body}
	\vspace{14pt}
	
	Armstrong, M., \textbf{Piccinini, P.}, Ritchart, A. (2016). ``Non-question rises in narratives produced by mothers and daughters." Poster presentation at Speech Prosody 8. Boston, MA. (May)\\
	\medskip
	
	Chung, Y., \textbf{Piccinini, P.}, Rose, S. (2016). ``The interaction of polar question and declarative intonation with lexical tone in Moro." Poster presentation at Speech Prosody 8. Boston, MA. (May)\\
	\medskip
	
	Tsuji, S.,  Lewis, M., Bergmann, C., Braginsky, M., \textbf{Piccinini, P.}, Frank, M. C., Cristia, A. (2016) ``MetaLab: Supporting power analysis and experimental planning in developmental research." Poster presentation at the XX International Conference on Infant Studies (ICIS). New Orleans, LA. (May)\\
	\medskip
	
	Bergmann, C., Tsuji, S., Lewis, M., Braginsky, M., \textbf{Piccinini, P.}, Cristia, A., Frank, M. C. (2016). ``MetaLab: Power analysis and experimental planning in developmental research made easy." Poster presentation at the 6th Budapest CEU Conference on Cognitive Development (BCCCD). Budapest, Hungry. (January)\\
	\medskip
	
	\textbf{Piccinini, P.}, Arvaniti, A. (2015). ``Voice onset time in Spanish-English spontaneous code-switching." Oral presentation at the 18th International Congress of Phonetic Sciences (ICPhS). Glasgow, Scotland. (August)\\
	\medskip
	
	Armstrong, M., \textbf{Piccinini, P.}, Ritchart, A. (2015). ``The phonetics and distribution of non-question rises in two varieties of American English." Poster presentation at the 18th International Congress of Phonetic Sciences (ICPhS). Glasgow, Scotland. (August)\\
	\medskip

	Pajak, B., \textbf{Piccinini, P.}, Levy, R. (2014). ``Perceptual warping of phonetic space applies beyond known phonetic categories: evidence from the perceptual magnet effect." Poster presentation at the 168th Meeting of the Acoustical Society of America (ASA). Indianapolis, IN. (October)\\
	\medskip

	\textbf{Piccinini, P.}, Garellek, M. (2014). ``Prosodic cues to monolingual versus code-switching sentences in English and Spanish." Poster presentation at Speech Prosody 7. Dublin, Ireland. (May)\\
	\medskip
	
	Davis, A., \textbf{Piccinini, P.}, Ribot, A. (2014). ``Catalan independence: Voluntary organizations and the construction of social capital." Oral presentation at the Symposium about Language and Society -- Austin (SALSA) XXII. Austin, TX. (April)\\
	\medskip
	
	\textbf{Piccinini, P.}, Arvaniti, A. (2014). ``The role of language dominance and language mode in speech processing by bilinguals.'' Poster presentation at the Meeting of the British Association of Academic Phoneticians. Oxford, UK. (April)\\
	\medskip

	\textbf{Piccinini, P.}, Arvaniti, A. (2014). ``Accessing cross language categories in exposure to a third language.'' Oral presentation at the 88th Annual Meeting of the Linguistic Society of America. Minneapolis, MN. (January)\\
	\medskip

	\textbf{Piccinini, P.} (2013). ``Predicting code-switches from phonetic information: The discourse marker \emph{like} in Spanish-English code-switching.'' Poster presentation at the 166th Meeting of the Acoustical Society of America (ASA). San Francisco, CA. (December)\\
	\medskip	

	\textbf{Piccinini, P.}, Arvaniti, A. (2013). ``Accessing cross language categories in learning a third language.'' Oral presentation at the 38th Annual Boston University Conference on Language Development. Boston, MA. (November)\\
	\medskip

	\textbf{Piccinini, P.}, Arvaniti, A. (2013). ``Accessing cross language categories in learning a third language.'' Poster presentation at the 2013 Linguistic Institute Workshop on Variation in the Acquisition of Sound Systems. Ann Arbor, MI. (June)\\
	\medskip
	
	\textbf{Piccinini, P.}, Kramer, E. (2013). ``Unsupervised machine learning for the accurate classification of the discourse marker \emph{like} in code-switching utterances.'' Poster presentation at the 21st Meeting of the International Congress on Acoustics (ICA) / the 165th Meeting of the Acoustical Society of America (ASA) /the 52nd Meeting of the Canadian Acoustical Association (CAA). Montreal, Canada. (June)\\
	\medskip
		
	Grijalva, C., \textbf{Piccinini, P.}, Arvaniti, A. (2013). ``The vowel spaces of Southern Californian English and Mexican Spanish as produced by monolinguals and bilinguals.'' Poster presentation at the 21st Meeting of the International Congress on Acoustics (ICA) / the 165th Meeting of the Acoustical Society of America (ASA) /the 52nd Meeting of the Canadian Acoustical Association (CAA). Montreal, Canada. (June)\\
	\medskip
			
	\textbf{Piccinini, P.} (2013). ``The predictive power of gradient phonetic cues in Spanish-English code-switching.'' Oral presentation at the 87th Annual Meeting of the Linguistic Society of America. Boston, MA. (January)\\
	\medskip
			
	\textbf{Piccinini, P.} (2012). ``The gradient production of Spanish-English code-switching.'' Poster presentation at the 86th Annual Meeting of the Linguistic Society of America. Portland, OR. (January)\\
	\medskip
			
	\textbf{Piccinini, P.} (2011). ``The production of Spanish-English code-switching.'' Poster presentation at the 162nd Meeting of the Acoustical Society of America (ASA). San Diego, CA. (November)\\
	\medskip
	
	\textbf{Piccinini, P.}, Arvaniti, A. (2011). ``The production of Spanish-English code-switching.'' Oral presentation at the 1st Meeting of Variation in Language Processing (VALP). Chester, UK. (April)\\
	\medskip	

	\textbf{Piccinini, P.}, Bradlow, A. (2011). ``Semantic contextual cues and listener adaptation to foreign-accented English.'' Oral presentation at the 1st Meeting of Variation in Language Processing (VALP). Chester, UK. (April)\\
	\medskip	

	\textbf{Piccinini, P.} (2009). ``Semantic contextual cues and listener adaptation to foreign-accented English.'' Poster presentation at the Northwestern Undergraduate Research Symposium. Evanston, IL. (faculty advisor Ann Bradlow) (May)\\
	\medskip	
	
	\textbf{Piccinini, P.}, Bradlow, A. (2009). ``Semantic contextual cues and listener adaptation to foreign-accented English.'' Poster presentation at the 2nd Special Workshop on Speech at the 157th Meeting of the Acoustical Society of America (ASA). Portland, OR. (May)\\
	\medskip
	
	\textbf{Piccinini, P.} (2009). ``Semantic contextual cues and listener adaptation to foreign-accented English.'' Poster presentation at the Chicago Area Undergraduate Research Symposium (CAURS). Chicago, IL. (faculty advisor Ann Bradlow) (April)\\
	
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fellowships and Research Grants
\header{Fellowships and Research Grants}

\begin{body}
	\vspace{14pt}
	
		\textbf{PhD Fellowship}, \'Ecole Doctorale Cerveau, Cognition, Comportement (ED3C) \hfill {} \emph{2015}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Modulation of cross-language activation in bilinguals\\
		\item[]\underline{Amount Awarded:} Declined\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
	
		\textbf{Claude Y. Vandeloise Fellowship}, Department of Linguistics, UC San Diego \hfill {} \emph{2014 - 2015}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Cross-language activation and the phonetics
of code-switching\\
		\item[]\underline{Amount Awarded:} \$3,909\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
	
	\textbf{Interdisciplinary Collaboratories Grant}, Office of the Chancellor, UC San Diego \hfill {} \emph{2013 - 2015}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Catalan independence: Voluntary organizations and the construction of social change\\
		\item[]\underline{Amount Awarded:} \$80,000 (jointly split with two other graduate student researchers)\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
		
	\textbf{NIH Pre-Doctoral Fellowship}, Center for Research in Language, UC San Diego \hfill {} \emph{2012 - 2013}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Bilinguals' abilities to use L1 and L2 categories in learning a 3rd language\\
		\item[]\underline{Amount Awarded:} \$31,832\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
	
	\textbf{Research Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2011}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Catalan-Spanish bilinguals' self-assessments of language proficiency\\
		\item[]\underline{Amount Awarded:} \$210\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
	
	\textbf{Weinberg Research Grant}, Weinberg College, Northwestern University \hfill {} \emph{2008}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} Bottom-up and top-down effects in foreign-accented speech recognition\\
		\item[]\underline{Amount Awarded:} \$3,000\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
	
	\textbf{Undergraduate Research Grant}, Weinberg College, Northwestern University \hfill {} \emph{2007}\\
	\vspace{-4pt}
	\begin{itemize}
		\item[]\underline{Project Funded:} A phonetic analysis of the Italian media's standard versus dialect uses\\
		\item[]\underline{Amount Awarded:} \$3,000\\
	\end{itemize}
	\vspace{-4pt}
	\medskip
		
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conference Travel Grants
\header{Conference Travel Grants}

\begin{body}
	\vspace{14pt}
	
	\textbf{IPA Student Award}, International Phonetic Association \hfill {} \emph{2015}\\
	\medskip
	
	\textbf{Bourses Doctorants}, GDR Neurosciences Cognitives du D\'eveloppement \hfill {} \emph{2015}\\
	\medskip
	
	\textbf{Elizabeth Bates Graduate Research Fund}, Center for Research in Language, UC San Diego \hfill {} \emph{2014}\\
	\medskip

	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2014}\\
	\medskip

	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2014}\\
	\medskip
	
	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2013}\\
	\medskip

	\textbf{Paula Menyuk Travel Award}, BU Conference on Language Development, Boston University \hfill {} \emph{2013}\\
	\medskip

	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2013}\\
	\medskip
	
	\textbf{Dean of Social Sciences Travel Grant}, Office of the Social Sciences, UC San Diego \hfill {} \emph{2013}\\
	\medskip
		
	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2012}\\
	\medskip
	
	\textbf{Conference Travel Grant}, Department of Linguistics, UC San Diego \hfill {} \emph{2011}\\
	\medskip
	
	\textbf{Weinberg Travel Grant}, Weinberg College, Northwestern University \hfill {} \emph{2009}\\
	\medskip
		
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}

	\textbf{Honorable Mention Student Poster Presentation in Speech Communication}, \hfill{} \emph{2013}\\
	166th Meeting of the Acoustical Society of America
	\medskip	

	\textbf{Honorable Mention Student Poster Presentation in Speech Communication}, \hfill{} \emph{2013}\\
	165th Meeting of the Acoustical Society of America
	\medskip	

	\textbf{TA Excellence Award}, Department of Linguistics, UC San Diego \hfill{} \emph{2012}\\
	\medskip

	\textbf{Best Poster Presentation in Social Science}, CAURS \hfill{} \emph{2009}\\
	\medskip
	
	\textbf{Demoz Prize}, Department of Linguistics, Northwestern University \hfill{} \emph{2008}\\
	\medskip
	
	\textbf{Distinguished Essay in English on an Italian Subject}, Northwestern University \hfill{} \emph{2007}\\
	
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching Experience
\header{Teaching Experience}

\begin{body}
	\vspace{14pt}
	
	\textbf{R for Publication}, Teacher, ENS DEC Life and online \hfill \emph{Winter 2016}\\
	\medskip

	\textbf{LIGN 17, Making and Breaking Codes}, Teaching Assistant, UC San Diego \hfill \emph{Winter 2014}\\
	\medskip	

	\textbf{LIGN 110, Phonetics}, Teaching Assistant, UC San Diego \hfill \emph{Fall 2013}\\
	\medskip
	
	\textbf{ANSC 113, Language, Style and Youth Identities}, Reader, UC San Diego \hfill \emph{Spring 2013}\\
	\medskip
	
	\textbf{LIGN 143, Structure of Spanish}, Teaching Assistant, UC San Diego \hfill \emph{Spring 2012}\\
	\medskip
	
	\textbf{LIGN/EDS 119, 1st and 2nd Language Acquisition}, Teaching Assistant, UC San Diego \hfill \emph{Winter 2012}\\
	\medskip
	
	\textbf{LIGN 110, Phonetics}, Teaching Assistant, UC San Diego \hfill \emph{Fall 2011}\\
	\medskip
	
	\textbf{LIGN 8, Languages and Cultures of America}, Teaching Assistant, UC San Diego \hfill \emph{Spring 2011}\\
	\medskip
	
	\textbf{LIGN/EDS 119, 1st and 2nd Language Acquisition}, Teaching Assistant, UC San Diego \hfill \emph{Winter 2011}\\
	\medskip
	
	\textbf{LIGN 101, Introduction to the Study of Language}, Teaching Assistant, UC San Diego \hfill \emph{Fall 2010}\\
	
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Undergraduate Mentorship
\header{Undergraduate Mentorship, University of California, San Diego}

\begin{body}
	\vspace{14pt}
	
	\textbf{Hilda Parra}, Research Assistant (faculty advisor: Marc Garellek) \hfill \emph{Fall 2015 - Fall 2015}\\
	\medskip
	
	\textbf{Gerardo Soto-Becerra}, Research Assistant (faculty advisor: Marc Garellek) \hfill \emph{Fall 2015 - Fall 2015}\\
	\medskip

	\textbf{Richard Kroeger}, Research Assistant (faculty advisor: Marc Garellek) \hfill \emph{Spring 2014 - Summer 2014}\\
	\medskip

	\textbf{Linnea Lagerstrom}, Research Assistant (faculty advisor: Marc Garellek) \hfill \emph{Fall 2013 - Summer 2014}\\
	\medskip

	\textbf{Esperanza Gonzalez}, Research Assistant (faculty advisor: Marc Garellek) \hfill \emph{Spring 2013 - Summer 2014}\\
	\medskip
	
	\textbf{Criccely Grijalva}, Research Assistant (faculty advisor: Amalia Arvaniti) \hfill \emph{Winter 2012 - Summer 2013}\\
	\medskip

	\textbf{Zully Herrarte}, Research Assistant (faculty advisor: Amalia Arvaniti) \hfill \emph{Fall 2012 - Spring 2013}\\
	\medskip
	
	\textbf{Mireya Pinell-Cruz}, Research Assistant (faculty advisor: Amalia Arvaniti) \hfill \emph{Winter 2012 - Spring 2012}\\
	\medskip
	
	\textbf{Rosa Quezada}, Research Assistant (faculty advisor: Amalia Arvaniti) \hfill \emph{Fall 2010}\\
	
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic Service
\header{Academic Service}

\begin{body}
	\vspace{14pt}
	
	\textbf{Member}, \#barbarplots Group and Kickstarter \hfill \emph{2016 - present} \\
	\medskip
	
	\textbf{Special Session Co-organizer}, Rising Intonation in English and Beyond, Speech Prosody 8 \hfill \emph{2016} \\
	\medskip
	
	\textbf{Reviewer}, Journal of the International Phonetic Association \hfill \emph{2014 - present} \\
	\medskip

	\textbf{Reviewer}, International Journal of Bilingualism Special Issue \hfill \emph{2013} \\
	\medskip
	
	\textbf{Research/Travel Grant Committee}, UC San Diego \hfill \emph{2013 - 2014} \\
	\medskip

	\textbf{Faculty Job Search Committee}, UC San Diego \hfill \emph{2012 - 2013} \\
	\medskip
	
	\textbf{Admissions Committee}, UC San Diego \hfill \emph{2011 - 2012} \\
	\medskip
	
	\textbf{Admissions Committee}, UC San Diego \hfill \emph{2010 - 2011} \\

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Affiliations and Memberships
\header{Affiliations and Memberships}

\begin{body}
	\vspace{14pt}
	
	\textbf{International Phonetic Association (IPA)} \hfill{} \emph{2015 - present}\\
	\medskip
	
	\textbf{Acoustical Society of America (ASA)} \hfill{} \emph{2009 - present}\\
	\medskip

	\textbf{Linguistic Society of America (LSA)} \hfill{} \emph{2009 - present}\\
	\medskip

\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Relevant Skills
\header{Relevant Skills}

\begin{body}
	\vspace{14pt}
	
	\textbf{Languages:} English (native), Spanish (conversational), Italian (conversational), French (beginner) Tun Savi Mixteco (field methods experience)\\
	\medskip
	
	\textbf{Programing Languages:} R, Python, Praat, MATLAB, LaTeX, CSS, HTML\\
	\medskip

	\textbf{Computer Programs:} Praat, PsychoPy, Superlab, Level16, NoiseMixer, Wavescroller, NU Aligner, HINT, StatView\\
	\medskip
	
	\textbf{Citizenships:} United States of America, Italy\\
	\medskip

\end{body}





























\end{document}
